From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-22 paper.tex
Robot with-me-ness computed
Commented out the heat-map for now

\subsubsection{Focus of attention distribution}

Additional information of the head pose can be obtained for the evaluation of
the VFoA distribution. Figure \ref{fig:heatmap} shows the most salient focuses
of attention where the peaks are located. These peaks are mainly projected
between the triangle composed by the robot, the writing tablet and the selection
tablet using an unsupervised K-means clustering method reveals, considering the
observers as negligible VFoA.

% Workaround to do subfigure since the packege looks not to work
\begin{figure}[th!]
  \centering
  \begin{tabular}{@{}c@{}}
    \includegraphics[width=.7\linewidth,height=100pt]{heatmap} \\
    \small (a)  2D histogram.
  \end{tabular}

  \begin{tabular}{@{}c@{}}
    \includegraphics[width=.7\linewidth,height=100pt]{kmeans} \\
    \small (b) K-means clustering.
  \end{tabular}

  \caption{ \small Subject 4 head movements. (head yaw on x-axis, pitch on y-axis).}
  \label{fig:heatmap}
\end{figure}

@@

\begin{table}[h!]
    \centering
    \caption{\textbf{Levels of with-me-ness}. For each subject, the with-me-ness level is reported over the whole interaction, either based on the ground-truth (\ie \emph{ground-truth with-me-ness}), or based on the focus of attention measured by the robot.}
    \begin{tabular}{p{1cm}cccccccc}
        \toprule
        Subject & 1 & 2 & 3 & 4 & 5 & 6 & Avg. & SD \\
        \midrule
        $\mathcal{W}_{g.truth}$ & 92.6 & 88.8  & 95.8 & 93.1 & 96.5 & 89.6 & 92.7 & 3.1 \\ 
        $\mathcal{W}_{robot}$ &  & & & & & & & \\
        \bottomrule
    \end{tabular}
    \label{tab:results-with-me-ness}
\end{table}

>>>>

%\subsubsection{Focus of attention distribution}
%
%Additional information of the head pose can be obtained for the evaluation of
%the VFoA distribution. Figure \ref{fig:heatmap} shows the most salient focuses
%of attention where the peaks are located. These peaks are mainly projected
%between the triangle composed by the robot, the writing tablet and the selection
%tablet using an unsupervised K-means clustering method reveals, considering the
%observers as negligible VFoA.
%
%% Workaround to do subfigure since the packege looks not to work
%\begin{figure}[th!]
%  \centering
%  \begin{tabular}{@{}c@{}}
%    \includegraphics[width=.7\linewidth,height=100pt]{heatmap} \\
%    \small (a)  2D histogram.
%  \end{tabular}
%
%  \vspace{\floatsep}
%
%  \begin{tabular}{@{}c@{}}
%    \includegraphics[width=.7\linewidth,height=100pt]{kmeans} \\
%    \small (b) K-means clustering.
%  \end{tabular}
%
%  \caption{ \small Subject 4 head movements. (head yaw on x-axis, pitch on y-axis).}
%  \label{fig:heatmap}
%\end{figure}

@@

\begin{table}[h!]
    \centering
    \caption{\textbf{Levels of with-me-ness}. For each subject, the with-me-ness level is reported over the whole interaction, either based on the ground-truth (\ie \emph{ground-truth with-me-ness}), or based on the focus of attention measured by the robot.}
    \begin{tabular}{p{1cm}cccccccc}
        \toprule
        Subject & 1 & 2 & 3 & 4 & 5 & 6 & Avg. & SD \\
        \midrule
        $\mathcal{W}_{g.truth}$ & 92.6 & 88.8  & 95.8 & 93.1 & 96.5 & 89.6 & 92.7 & 3.1 \\ 
        $\mathcal{W}_{robot}$ & 89.6 & 84.4 & 86.6 & 72.8 & 81.9 & 79.7 & 82.5 & 5.4 \\
        \bottomrule
    \end{tabular}
    \label{tab:results-with-me-ness}
\end{table}
